---
title: "DV_RProject1"
author: "Kayne Khoury, Zareen Khayrattee, Juanito Taveras"
date: "September 15, 2015"
output: html_document
---
----------------

#Plot 1
SQL: select * where from titanic
```{r}
source("../02 Visualizations/plot1.R",echo=TRUE)
```
#Plot 2
SQL: select * where from titanic where sex is not null
```{r}
source("../02 Visualizations/plot2.R",echo=TRUE)
```
#Plot 3
SQL: select * where from titanic where sex is not null
```{r}
source("../02 Visualizations/plot3.R",echo=TRUE)
```
#Plot 4
SQL: select * where from titanic where sex is not null
```{r}
source("../02 Visualizations/plot4.R",echo=TRUE)
```
#Plot 5
SQL: select * where from titanic where sex is not null and age <= 10
```{r}
source("../02 Visualizations/plot5.R",echo=TRUE)
```
#Plot 6
SQL: select * where from titanic where sex is not null and age > 50
```{r}
source("../02 Visualizations/plot6.R",echo=TRUE)
```
#Summary
SQL: select * where from titanic where sex is not null
```{r}
source("../01 Data/summary.R",echo=TRUE)
```
#Subset
SQL: select * where from titanic where sex is not null
```{r}
source("../01 Data/subset.R",echo=TRUE)
```
